Milestone 2: Datasets Generation

### 2019-10-24 perf_release_criteria/milestone_3/ms_2_dataset_generation.Rmd
Adding nn experiment.

```{r bootstrap_def}
extract_ids <- function(df_c, size, oversampling){
  df_beta <- df_c %>% filter(is_release == FALSE)
  df_rel <- df_c %>% filter(is_release == TRUE)
  n_beta <- nrow(df_beta)

>>>>

```{r bootstrap_def}
extract_ids <- function(df_c, oversampling){
  df_beta <- df_c %>% filter(is_release == FALSE)
  df_rel <- df_c %>% filter(is_release == TRUE)
  n_beta <- nrow(df_beta)
